Methods paper for erosion

### 2018-01-04 docs/methods/erosion_methods.tex
started working on intro again ...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}

\paragraph{Contributions}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Erosion by flowing fluid plays an essential role in diverse processes.
Many of the flows are geophysical, such as the formation of sand dunes
or erosion due to groundwater flow.  In both these examples, there is a
feedback process between the flow and the erodible body.  In particular,
the shape of the eroding body affects the flow, while the flow changes
the shape of the eroding body.

\paragraph{Contributions} The present study will develop numerical
methods to simulate viscous erosion of a multiply-connected
two-dimensional geometry.  By assuming the flow is viscous, we are
assuming the flow is very slow, such as in groundwater flow.  Moreover,
by allowing for complex multiply-connected domains, the erosion caused
by the non-local complex interactions between different bodies is
modeled.

Because of the low Reyonlds number assumption, the flow will be assumed
to be Stokesian.  Then, to create high-fidelity and computationally
efficient numerical methods, two fast and accurate methods will be
employed:
\begin{enumerate}
  \item The fluid equations will be solved with spectral accuracy by
  using an efficient boundary integral equation method. Moreover, the
  rate of erosion will be computed and the rate of erosion will be
  computed with spectral accuracy.
  \item Given a rate of erosion, the shape will be integrated in time
  with second-order accuracy.  All spatial derivatives will be computed
  in Fourier space, resulting in spectral accuracy in space.
\end{enumerate}
